Katana: A Userland Toolchain-Oriented Hotpatching System

### 2010-11-23 doc/katana.tex
updated documentation

% Created 2010-06-22 Tue 19:27
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{22 June 2010}

@@

   \texttt{katana -g [-o OUTPUT\_FILE] /project/v0 /project/v1 foo}

@@

   \texttt{katana -g [-o OUTUT\_FILE] OLD\_OBJECTS\_DIR NEW\_OBJECTS\_DIR EXECUTABLE\_NAME}

@@

   \texttt{katana -p [-s] PATCH PID}

@@

   \texttt{katana -l PATCH}
\subsection{See Also}
\label{sec-6.5}

   the katana manpage (once it's written, which it is not yet)
\section{Patch Object Format}
\label{sec-7}

@@

  This section of the document is not yet written. It will provide a
  description of the internal process that Katana uses to generate a
  patch. Understanding it is not necessary for using Katana.
\section{Patch Application Process}
\label{sec-9}

>>>>

% Created 2010-11-14 Sun 15:47
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{soul}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx}

\title{Katana: A Userland Toolchain-Oriented Hotpatching System}
\author{James Oakley}
\date{14 November 2010}

@@

   \texttt{katana [OPTIONS] -g [-o OUTPUT\_FILE] /project/v0 /project/v1 foo}

@@

   \texttt{katana [OPTIONS] -g [-o OUTUT\_FILE] OLD\_OBJECTS\_DIR NEW\_OBJECTS\_DIR EXECUTABLE\_NAME}

@@

   \texttt{katana [OPTIONS] -p [-s] PATCH PID}

@@

   \texttt{katana [OPTIONS] -l PATCH}
\subsection{Options}
\label{sec-6.5}

   The following options may be passed to katana regardless of whether
   one is generating, applying, or viewing a patch:
\begin{itemize}
\item -c CONFIG
     where CONFIG is the name of a configuration file to load
\end{itemize}
\subsection{Configuration Files}
\label{sec-6.6}

   Katana loads configuration files as follows. Configuration files
   loaded later in the sequence may overwrite settings from files
   earlier in the sequence.
\begin{itemize}
\item \emph{etc/katana    + \~{}}.katana
\item \~{}/.config/katana
\item ./katana
\item any file specified with -c
\end{itemize}
   Configuration files are written in JSON. The JSON requirement that
   strings be quoted is relaxed (i.e. anything is assumed to be a
   string unless it can be interpreted otherwise). The following
   properties are recognized:
\begin{itemize}
\item maxWaitForPatching <INTEGER>
     This value specifies the maximum number of seconds to wait for
     the target to enter a safe state.
\item flags <OBJECT>
     The value of flags should be an object which may contain the
     following properties, all of which should be bool-valued:

\begin{itemize}
\item checkPtraceWrites
       Whenever something is written into the target memory, read the
       value back out and verify that it was written correctly. This
       has a performance penalty, but does provide some more robust
       error checking, although it should not be necessary.
\end{itemize}

\end{itemize}
\subsection{See Also}
\label{sec-6.7}

   the katana manpage (although the information in this document is
   considerably more extensive than in the manpage)
\section{Patch Object Format}
\label{sec-7}

@@

  This section of the document is still under construction. When
  complete, it will provide a description of the internal process that
  Katana uses to generate a patch. Understanding it is not necessary
  for using Katana.

\subsection{Configuration}
\label{sec-8.1}

   Katana reads configuration files from (in order, with later
   configuration files overriding options found in earlier ones) from
   \texttt{/etc/katana}, \texttt{\textasciitilde{}/.katana}, \texttt{\textasciitilde{}/.config/katana}, and \texttt{./.katana}.

\subsection{Initializing the patch object}
\label{sec-8.2}

   Katana sets up a patch object ELF file with the necessary sections,
   see \hyperref[sec-7]{Patch Object Format}
\subsection{Comparing source trees}
\label{sec-8.3}

\begin{itemize}
\item Katana compare the old and new source trees, looking at the object (.o)
     files.
\item For object files which exist only in the new tree, their contents
     are added to the patch object being created.
\item For object files which exist only in the old tree, a warning
     about their removal is issued and nothing further is done.
\item For object files which exist in both trees, type diffing and
     function diffing are performed and the differences are written
     tot he patch object being created.
\end{itemize}
\section{Patch Application Process}
\label{sec-9}
